Increased Education Level of Women Associates with Higher Occupational Prestige and Happiness

### 2023-03-16 outputs/paper/paper.qmd
added results section

sum up all 3 graphs here

>>>>

Figure 1 shows an increase in mean highest education level, Figure 2 shows an increase in mean occupational prestige percentage and Figure 3 shows an increase in overall happiness. This means that at a slow and steady rate, women are acquiring better education, getting better jobs and becoming happier. The findings show that there is a positive relationship between job prestige, education and happiness. Just do these three factors tie into one another?
